FinalManuscript_DISCS_UG

### 2018-10-07 parts/02_relatedliterature.tex
RRL summary and fixes
- Commented out spatial filter section
- Updated summary to reflect new research
- Fixed some typesetting errors in D-P section

\section{Summary}
We have seen how various image processing operations make use of a series of additions and multiplications. Because of this, it is possible to use a homomorphic cryptosystem in order to apply image operations directly on encrypted images, as demonstrated by the \textit{CryptoImg} library.

In particular, we aim to address the shortcomings of \textit{CryptoImg} by developing a library to test various homomorphic encryption schemes with the help of the \textit{HElib} library to be able to implement fully homomorphic encryption schemes efficiently. This helps us determine the practicality of using homomorphic cryptosystems in image processing, especially when dealing with more complex image operations.

>>>>

\section{Summary}
We have seen how privacy-preserving image operations have been implemented in the literature using partially homomorphic cryptosystems. \textit{CryptoImg} provided a suite of linear image processing operations using the Paillier cryptosystem, while Erkin, et al. have implemented a privacy-preserving version of the eigenfaces approach to facial recognition developed by Turk and Pentland.

We have presented as well several areas in which our study will expand on the research so far.
\begin{enumerate}
  \item We have shown two fully homomorphic cryptosystems, the Dasgupta-Pal cryptosystem and the BGV cryptosystem. While these cryptosystems are generally less efficient than partially homomorphic cryptosystems, they do not require additional protocols for exponentiation.
  \item Due to the general limitations of partially homomorphic systems, attempts at applying homomorphic cryptography to applications such as image processing and facial recognition have mainly been restricted to linear operations on ciphertext. We have shown that there are basic image processing operations which are non-linear, which we can implement.
  \item While privacy-preserving facial recognition has been accomplished by Erkin, et al., privacy-preserving facial detection is an area of research which has yet to explored.
\end{enumerate}

### 2018-10-07 parts/02_relatedliterature_02commonimageprocessingoperations.tex
RRL summary and fixes
- Commented out spatial filter section
- Updated summary to reflect new research
- Fixed some typesetting errors in D-P section

\section{Image Processing Operations}
The \textit{CryptoImg} library implemented several
We discuss two basic types of image processing operations, \textit{intensity transformations}, which map an intensity value to another, and \textit{spatial filters} which consider intensity values from regions of pixels to perform operations such as edge detection, image blurring and sharpening.

We represent a digital image $R$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$. We use $R(x,y)$ represents the entry at the $x$th row and $y$th column of a matrix $R$.

\subsection{Intensity Transformations}
An Intensity transformation on an image $R$ can be defined as a function $T$ which maps a pixel value $r$ to a new value $r^\prime$, which we can write as $r^\prime = T\left(r\right)$. This function is then applied to every pixel in $R$.

The \textit{CryptoImg} library implemented two types of linear intensity transformations: image negation and brightness control.
An image negation transformation is defined as:
\begin{equation}
    T\left(r\right) = L-1-r
\end{equation}
After applying image negation, the resulting image would be similar to a photographic negative~\cite{gonzalez_digital_2008}.

@@

To implement non-linear intensity transformations using addition and multiplication in a homomorphic system, it is necessary to approximate the logarithm and exponential functions, which may result in higher computational overhead. In our software library implementation, we investigate methods required to approximate the logarithm and functions.

\subsection{Spatial Filtering}
The \textit{CryptoImg} library also implemented \textit{spatial filters}. Spatial filters are operators which determine output pixels using information from neighboring input pixels. To apply a spatial filter to obtain a resulting image $R^\prime$, a convolution is performed between an $m \times n$ matrix $k$, called a kernel, and the original $M\times N$ image $R$.
A convolution between a kernel $k$ and image $R$ which yields a resulting image $R^\prime$, denoted as $R^\prime = k \ast R$, is defined by
\begin{align} \label{eq:spatialfilter}
	R^\prime(x,y) = \sum_{s=1}^m{\sum_{t=1}^n{k(s,t)R(x+s,y+t)}}, \text{ for all } 0\leq x \leq M, 0 \leq y \leq N,
\end{align}

@@

%% TODO: specific list of kernels to use for this study

>>>>

%We discuss two basic types of image processing operations, \textit{intensity transformations}, which map an intensity value to another, and \textit{spatial filters} which consider intensity values from regions of pixels to perform operations such as edge detection, image blurring and sharpening.

\section{Image Intensity Transformations}
We represent a digital image $R$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$. We use $R(x,y)$ represents the entry at the $x$th row and $y$th column of a matrix $R$.
An intensity transformation on an image $R$ can be defined as a function $T$ which maps a pixel value $r$ to a new value $r^\prime$, which we can write as $r^\prime = T\left(r\right)$. This function is then applied to every pixel in $R$.
The \textit{CryptoImg} library implemented two types of linear intensity transformations: image negation and brightness control.

An image negation transformation is defined as:
\begin{equation}
    T\left(r\right) = L-1-r
\end{equation}
After applying image negation, the resulting image would be similar to a photographic negative~\cite{gonzalez_digital_2008}.

@@

To implement non-linear intensity transformations using addition and multiplication in a homomorphic system, it is necessary to approximate the logarithm and exponential functions, which may result in higher computational overhead. In our software library implementation, we investigate methods required to approximate the logarithm and power functions. Non-linear intensity transformations such as the logarithm transformation have applications in intensity normalization \cite{oravec_illumination_2010}, which is used in some facial recognition algorithms to account for differences in lighting which make facial recognition difficult.

\begin{comment}
\subsection{Spatial Filtering}
The \textit{CryptoImg} library also implemented \textit{spatial filters}. Spatial filters are operators which determine output pixels using information from neighboring input pixels. To apply a spatial filter to obtain a resulting image $R^\prime$, a convolution is performed between an $m \times n$ matrix $k$, called a kernel, and the original $M\times N$ image $R$.
A convolution between a kernel $k$ and image $R$ which yields a resulting image $R^\prime$, denoted as $R^\prime = k \ast R$, is defined by
\begin{align} \label{eq:spatialfilter}
	R^\prime(x,y) = \sum_{s=1}^m{\sum_{t=1}^n{k(s,t)R(x+s,y+t)}}, \text{ for all } 0\leq x \leq M, 0 \leq y \leq N,
\end{align}

@@

%% TODO: specific list of kernels to use for this study
\end{comment}

### 2018-10-07 parts/02_relatedliterature_06fullyhomomorphic.tex
RRL summary and fixes
- Commented out spatial filter section
- Updated summary to reflect new research
- Fixed some typesetting errors in D-P section

Given a message $m \in \mathbb{n}$, we denote
\begin{align*}
		m_p(x) = a_0 + a_1x + a_2x^2 + \cdots + a_kx^k
\end{align*}
where $a_ka_{k-1}\cdots a_2a_1_0$ is the binary representation of $m$.

In the original scheme presented in \cite{dasgupta_design_2016}, the secret key $S_k$ is set to be a large prime. In Appendix \autoref{ch:correction}, we present a case where the Dasgupta-Pal cryptosystem fails and prove that setting the secret key $S_k = 2p$, where $p$ is a large prime, corrects errors in the Dasgupta-Pal cryptosystem.
We now decribe the correct cryptosystem.
\subsubsection{Corrected Dasgupta-Pal Cryptosystem Description}
Let $\ell$ denote the security parameter of the cryptosystem.
Let $S_k = 2p$, where $p$ is a prime number with $\ell - 1$ bits.
Choose a random even integer $z$ of length $\log_2{\ell}$.

@@

Furthermore, the decryption algorithm to recover $m_p(x)$ from a ciphertext polynomial $c(x)$ as
\begin{align*}
	m_p(x) = c(x) \bmod S_k \bmod 2
\end{align*}
Thus $D(c(x))$ is defined as the integer recovered from the coefficients of the polynomial $c(x) \bmod S_k \bmod 2$

Dasgupta and Pal note that homomorphic operations on ciphertext introduce noise which may interfere with decryption, due to the potential increase in ciphertext values.
To eliminate noise from a polynomial ciphertext, the following refresh function is used.
\begin{align*}
	R(c(x)) = c(x) \bmod R_k
\end{align*}

\subsubsection{Homomorphic Properties of the Dasgupta-Pal Cryptosystem}
It has been shown \cite{dasgupta_design_2016} that the following properties hold for all integer messages $m_1, m_2 \in \mathbb{Z}_n$ in the Dasgupta-Pal cryptosystem. These properties arise since each coefficient in a ciphertext polynomial is essentially an independently encrypted bit of the original message.
\begin{description}
	\item[XOR on ciphertexts]
	A bitwise exclusive or (XOR) operation on integer messages can be achieved by adding the coefficients pairwise between two ciphertexts.
	\begin{align*}
		D(E(m_1)+E(m_2)) = m_1 \text{ XOR } m_2
	\end{align*}
	\item[AND on ciphertexts]
	Similarly, pair-wise multiplication corresponds to bitwise AND of integer messages.
	\begin{align*}
		D(E(a) \otimes E(b)) = a \text{ AND } b = ab \bmod 2
	\end{align*}
	where $\otimes$ denotes pairwise multiplication,
	\begin{align*}
		\sum_{i=1}^n{a_ix^i} \otimes \sum_{i=1}^n{b_ix^i} = \sum_{i=1}^n{a_ib_ix^i}.
	\end{align*}
\end{description}
Arbitrary computation on data can thus be achived using these bitwise operations.

@@

The details regarding the construction of the BGV cryptosystem are beyond the scope of this paper. For this study, we will be using \textit{HElib} \cite{garay_algorithms_2014}, an open-source library which implements the BGV cryptosystem with optimizations to improve efficiency \cite{hutchison_fully_2010,cryptoeprint:2011:566}.

>>>>

Given a message $m \in \mathbb{Z}$, we denote
\begin{align*}
		m_p(x) = a_0 + a_1x + a_2x^2 + \cdots + a_kx^k
\end{align*}
where $a_ka_{k-1}\cdots a_2a_1_0$ is the binary representation of $m$.

In the original scheme presented in \cite{dasgupta_design_2016}, the secret key $S_k$ is set to be a large prime. In Appendix \ref{chap:correction}, we present a case where the Dasgupta-Pal cryptosystem fails and prove that setting the secret key $S_k = 2p$, where $p$ is a large prime, corrects errors in the Dasgupta-Pal cryptosystem.
We now decribe the correct cryptosystem.
\subsubsection{Corrected Dasgupta-Pal Cryptosystem Description}
Let $\ell$ denote the security parameter of the cryptosystem.
Let $S_k = 2p$, where $p$ is a prime number with $\ell - 1$ bits.
Choose a random even integer $z$ of length $\log_2{\ell}$.

@@

Furthermore, the decryption algorithm to recover $m_p(x)$ from a ciphertext polynomial $c(x)$ as
\begin{align*}
	m_p(x) = c(x) \bmod S_k \bmod 2.
\end{align*}
Thus $D(c(x))$ is defined as the integer recovered from the coefficients of the polynomial $c(x) \bmod S_k \bmod 2$.

Dasgupta and Pal note that homomorphic operations on ciphertext introduce noise which may interfere with decryption, due to the potential increase in ciphertext values.
To eliminate noise from a polynomial ciphertext, the following refresh function is used:
\begin{align*}
	R(c(x)) = c(x) \bmod R_k.
\end{align*}

\subsubsection{Homomorphic Properties of the Dasgupta-Pal Cryptosystem}
It has been shown \cite{dasgupta_design_2016} that the following properties hold for all integer messages $m_1, m_2 \in \mathbb{Z}_n$ in the Dasgupta-Pal cryptosystem. These properties arise since each coefficient in a ciphertext polynomial is essentially an independently encrypted bit of the original message.
\begin{description}
	\item[XOR on ciphertexts]
	A bitwise exclusive or (XOR) operation on integer messages can be achieved by adding the coefficients pairwise between two ciphertexts.
	\begin{align*}
		D(E(m_1)+E(m_2)) = m_1 \text{ XOR } m_2
	\end{align*}
	\item[AND on ciphertexts]
	Similarly, pair-wise multiplication corresponds to bitwise AND of integer messages.
	\begin{align*}
		D(E(a) \otimes E(b)) = a \text{ AND } b = ab \bmod 2
	\end{align*}
	where $\otimes$ denotes pairwise multiplication,
	\begin{align*}
		\sum_{i=1}^n{a_ix^i} \otimes \sum_{i=1}^n{b_ix^i} = \sum_{i=1}^n{a_ib_ix^i}.
	\end{align*}
\end{description}

Arbitrary computation on data can thus be achived using these bitwise operations. While the Dasgupta-Pal cryptosystem requires significant amounts of memory, as each bit of plaintext is encrypted into an integer, this approach provides a flexible method to perform relatively fast arbitrary computation on encrypted data. Encryption and decryption in the Dasgupta-Pal cryptosystem are accomplished using few arithmetic operations.

@@

The details regarding the construction of the BGV cryptosystem are beyond the scope of this paper. For this study, we will be using \textit{HElib} \cite{garay_algorithms_2014}, an open-source library which implements the BGV cryptosystem with optimizations to improve efficiency. Evaluation of operations on 120 inputs in HELib was performed in around 4 minutes, with an average of 2 seconds to process a single input \cite{hutchison_fully_2010,cryptoeprint:2011:566}.
